Metric Spaces with Expensive Distances

### 2018-12-05 paper/draft.tex
interim

\section{Experiments on spanners}
At the moment we cannot provide any theoretical guarantees for the heuristics that we propose to compute blind spanners,
and it can happen that it will yield the complete graph as a spanner.
We run experiments on the points sampled from the low-dimensional Euclidean space to investigate
experimentally the performance of these heuristics. Clearly, this has no practical meaning for $\R^d$, but
this space is well-suited for controlled experiments.

@@

\subsection{Experiments on approximate nearest neighbors}

>>>>

\section{Experiments on spanners}
We run experiments on the points sampled from the low-dimensional Euclidean space to investigate
experimentally the performance of these heuristics. Clearly, this has no practical meaning for $\R^d$, but
this space is well-suited for controlled experiments.

@@

\section{Experiments on approximate nearest neighbors}
